Kelompok 4_Praktikum_Pekan 8

### 2024-04-06 Project/Kelompok 4_Praktikum_Pekan 8.Rmd
Update

install_load("fitdistrplus","ggplot2","gridExtra")
```

@@

```{r}
plot_distribution <- function(data, title) {
  df <- data.frame(x = data)
  p1 <- ggplot(data = df, aes(x = x)) +
    geom_histogram(bins = 20, fill = "blue", alpha = 0.7) +
    geom_density(aes(y = ..count..), fill = "red", alpha = 0.4) + # Poligon densitas
    labs(title = paste("Histogram", title)) +
    theme_minimal()

  grid.arrange(p1, p2, ncol = 2)
}

for (size in sample_sizes) {
  samples <- list(
    "Mixed Data 1" = mixed_data_1,
    "Mixed Data 2" = mixed_data_2,
    "Mixed Data 3" = mixed_data_3
  )
  for (title in names(samples)) {
    sample <- sample(samples[[title]], size, replace = FALSE)
    plot_distribution(sample, paste0(title, " (n=", size,")"))
  }
}
```

```{r}
plot_distribution <- function(data, title) {
  df <- data.frame(x = data)
  p1 <- ggplot(data = df, aes(x = x)) +
    geom_histogram(bins = 20, fill = "blue", alpha = 0.7) +
    geom_density(aes(y = ..count..), fill = "red", alpha = 0.4) + # Poligon densitas
    labs(title = paste("Histogram", title)) +
    theme_minimal()

@@

  for (title in names(samples)) {
    sample <- sample(samples[[title]], size, replace = FALSE)
    plots <- plot_distribution(sample, paste0(title, " (n=", size,")"))
    plots_for_size <- c(plots_for_size, plots)
  }

@@

# Menggabungkan semua plot menjadi satu menggunakan cowplot
library(cowplot)
plot_grid(plotlist = all_plots, ncol = 2)
```

>>>>

install_load("fitdistrplus","ggplot2","gridExtra","cowplot")
```

@@

```{r fig.height=20, fig.width=25, dpi=300}
sample_sizes <- c(4, 12, 20, 60, 100)

plot_distribution <- function(data, title, color) {
  df <- data.frame(x = data)
  p1 <- ggplot(data = df, aes(x = x)) +
    geom_histogram(bins = 20, fill = color, alpha = 0.7) +
    geom_density(aes(y = ..count..), fill = color, alpha = 0.4) + # Poligon densitas
    labs(title = paste("Histogram", title)) +
    theme_minimal()

@@

  colors <- c("blue", "green", "orange")  # warna yang berbeda untuk setiap jenis mixed data

  for (i in 1:length(samples)) {
    title <- names(samples)[i]
    sample <- sample(samples[[title]], size, replace = FALSE)
    plots <- plot_distribution(sample, paste0(title, " (n=", size,")"), colors[i])
    plots_for_size <- c(plots_for_size, plots)
  }

@@

# Menggabungkan semua plot menjadi satu menggunakan cowplot
library(cowplot)
plot_grid(plotlist = all_plots, ncol = 6)
```
